### 2016-07-05 image_setup.tex
Some edits

The root filesystem mounted in \texttt{ROOTDIR}, already has a boot
directory that can be used as the mount point for the boot partition
in the block device \texttt{loop0p1}. This is convenient because
the final edited partition from \texttt{ROOTDIR/boot} will be mounted on
this same directory when a \ac{Raspi} starts up with a memory card
containing the raw final image. Hence, to mount boot partition we do:
%It is therefore the natural place to mount it for later purposes.

@@

The \ac{Raspi}s should be setup as similar as possible. One of those
few settings that may be different in the devices is their hostname.
%The hostname helps the user to distinguish the devices from each other.
%The hostname helps distinguish them from each other.
One approach to create unique hostnames would be to write the hostname
in each memory card. Another way is to create a start up script to automatically
configure the hostname. We decided to define the hostnames based on the \ac{MAC}
addresses of the \ac{Raspi}s wired ethernet interface. We store the \ac{MAC}
addresses and hostnames of the \ac{Raspi}s in a file as below. The testbed
administrator will need to insert the \ac{MAC} addresses and hostnames of
his/her \ac{Raspi}s.

@@

Finally, it is time to change root.
%Finally, the filesystem is ready for us to change root.
This can be done with \texttt{proot}. It may be required to install \texttt{proot}
using "\texttt{apt-get install proot}":

>>>>

The root filesystem mounted in \texttt{ROOTDIR}, has already a boot
directory that can be used as the mount point for the boot partition
in the block device \texttt{loop0p1}. This is convenient because
the final edited partition from \texttt{ROOTDIR/boot} will be mounted on
this same directory when a \ac{Raspi} starts up with a memory card
containing the raw final image. Hence, to mount boot partition we do:
%It is therefore the natural place to mount it for later purposes.

@@

In general, the \ac{Raspi}s should be setup as similar as possible. However,
some particularities exist to differentiate the devices in principle
One of those
few settings that may be different in the devices is their hostname.
%The hostname helps the user to distinguish the devices from each other.
%The hostname helps distinguish them from each other.
One approach to create unique hostnames would be to write the hostname
in each memory card. Another way is to create a start up script to automatically
configure the hostname. We decided to define the hostnames based on the \ac{MAC}
addresses of the \ac{Raspi}s wired ethernet interface. We store the \ac{MAC}
addresses and hostnames of the \ac{Raspi}s in a file as below. The testbed
administrator will need to insert the \ac{MAC} addresses and hostnames of
his/her \ac{Raspi}s.

@@

Finally, it is time to change root.
%Finally, the filesystem is ready for us to change root.
This can be done with \texttt{proot}. It may be required to install
\texttt{proot} using \texttt{apt-get install proot}:
